Robust Spectroscopic Inference with Imperfect Models

### 2014-08-27 tex/paper.tex
Figure updates

>>>>

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_Kurucz_logg.pdf}
\caption{A sample of the WASP-14 data set overlaid with a model spectrum produced by parameters drawn from the posterior probability distribution (fixing $\log_{10} g = 4.29$ dex) and using the {\sc CfA/Kurucz} synthetic library. The residuals are shown zoomed along with the three-sigma contours of random draws from the covariance matrix, after Figure~\ref{fig:matrix}.}
\label{fig:Kurucz_residuals}
\end{center}
\end{figure*}
